SI

### 2021-02-01 ms/si.Rmd
WIP: add SI figure showing range comparison between G and S

```{r si-load-data, cache = FALSE}
tar_load(filmy_dt_chamber)
tar_load(filmy_dt)
tar_load(filmy_habit)
tar_load(rel_water_indiv)
tar_load(rel_water_species_means)
tar_load(filmy_phy)
tar_load(filmy_habit)
```

@@

# Define color-blind palette
cbPalette <- c(grey = "#999999", gold = "#E69F00", skyblue = "#56B4E9", 
               green = "#009E73", yellow = "#F0E442", blue = "#0072B2", 
               red = "#D55E00", purple = "#CC79A7")
```

@@

\clearpage

@@

\clearpage

@@

@@

\clearpage

\clearpage

>>>>

```{r si-load-data, cache = FALSE}
tar_load(filmy_dt_chamber)
tar_load(filmy_dt)
tar_load(filmy_habit)
tar_load(rel_water_indiv)
tar_load(rel_water_species_means)
tar_load(filmy_phy)
tar_load(filmy_habit)
tar_load(range_comparison)
```

@@

# Define color-blind palette
cbPalette <- c(grey = "#999999", gold = "#E69F00", skyblue = "#56B4E9", 
               green = "#009E73", yellow = "#F0E442", blue = "#0072B2", 
               red = "#D55E00", purple = "#CC79A7")

# Set colors for growth habit, generation
habit_colors <- c(
  "Terrestrial" = cbPalette[["red"]], 
  "Saxicolous" = cbPalette[["gold"]], 
  "Low_Epiphyte" = cbPalette[["green"]],
  "High_Epiphyte" = cbPalette[["blue"]])
```

@@

\newpage

@@

\newpage

\newpage

```{r range-plot, fig.height = 4.5, fig.width = 7, fig.cap = ""}
range_comparison %>%
  left_join(filmy_habit, by = "species") %>%
  mutate(species = factor(species) %>% fct_reorder(sporo_min_range)) %>%
  ggplot(aes(y = species)) +
  geom_linerange(aes(xmin = gameto_min_range, xmax = gameto_max_range)) +
  geom_linerange(aes(xmin = sporo_min_range, xmax = sporo_max_range, color = habit), size = 3) +
  geom_point(
    data = filter(range_comparison, gameto_min_range < sporo_min_range), 
    aes(x = gameto_min_range)) +
  geom_point(
    data = filter(range_comparison, gameto_max_range > sporo_max_range),
    aes(x = gameto_max_range)) +
  scale_color_manual(values = habit_colors, labels = pretty_text) +
  labs(x = "Elevation (m)", y = "Species") +
  theme(
    legend.position = "bottom"
  )
```

**`r s_figure("range")`**. Elevational range of sporophytes and gametophytes of filmy ferns on Moorea, French Polynesia. Observed elevational range width of sporophytes shown with colored bars; range of gametophytes occuring beyond sporophytes shown with lines and dots. Color indicates growth habit.

@@

\newpage

\newpage

@@
